\begin{itemize}[noitemsep]
    \item asd1
    \item asd2
    \item asd3
\end{itemize}
What is an API?
An API is like a library for programmers. A good API will make it possible for the programmer to use certain functions or procedures from a different application without understanding the underlying implementation or structure of this different application.

More to come…
%%\url{https://en.wikipedia.org/wiki/Application_programming_interface}


Which APIs would be interesting in respect to our project
An interesting API which is relevant for our project is the John Deere’s Agricultural API called MyJohnDeere API.
The MyJohnDeere API mentions on their website that their API is capable of providing information such as:
Transfer Data, Agronomic Data, Field Condition, Machine Monitoring, Logistics Data.

When you are using John Deere equipment and you’ve completed a field operation, documentation is sent to John Deere Operation Center. Most of the data that can be retrieved from their API is from this Operation Center.

It is possible to retrieve information about specific costumers, but keep in mind that it is not possible to retrieve information about any costumers without being granted permission. 
Another Note: An EIC license is required to decode display data. So in order to use MyJohnDeere API fully, such a license is required.
Quote
“Note: When an app is connected to this API in Sandbox, only users within the app team will be able to successfully call the API. Users outside of the app team who use the application to call the API will receive a 403 Error.”

% Comments