In this section we will figure out what OS (Operating System) that are available for tablets nowadays and what makes the individual OS great and/or bad. This section should help us towards picking a final OS on which our application would be developed for. 
A very big part of the tablet is the Operating system (OS). There's quite a bunch of different OS's we will be listing the most popular systems and explain what makes them individually good or bad.

\textbf{iOS}\newline
The most recent version of Apple's iOS as of this time of writing is iOS 10. It is developed by the American hardware \& software manufacturer Apple. iOS is an operating system that is being used by all of Apple's mobile products, such as their iPad and iPhone products. iOS 10 was released September 13th\cite{macworld:iosreleasedate} with much criticism and complaints from apple-fans and critics alike. Apple made a lot of drastic changes to features such as the lock-screen that many users didn't agree with. Looking past the recent criticisms Apple has made a very robust operating system that does everyday tasks quickly and is very intuitive to use. Their main focus has been on usability and useability rather than extendability and customization. It is a closed system, which means that Apple have locked users away from their local file system except for personal files such as photos, videos, music files etc. Because of this, iOS is also almost safe for viruses and hacking attacks, though there have been popping up more and more exploits\cite{xiao:claud} with each iteration of the system. 
From a development standpoint iOS has previously had a relatively high barrier to entry, since you couldn't just freely build software onto an Apple iOS product. You had to have a registered Apple Developer account, where the cheapest version currently is \$99 USD for a years developer membership. But now Apple offer a student programme and anyone with an Apple ID can build and upload an application to their personal iOS device. You won't be able to upload to Apple's App Store without having a registered developer account\cite{apple:developerprogram}. 

% Mål for afsnit.. 
%   - Finde ud af pros & Cons hos de forskellige OS'er
%   
%% Android - (Manufactures (bliver skrevet om i tablet teknologi afsnittet))
\textbf{Android}\newline % bla bla bla. Android has a tendency to name their versions off of candy.
Android has traditionally named their versions after sweets or cakes, which is also apparent in the most recent iteration, Android 7.0 "Nougat", released the 22. of August 2016\cite{android:latest_version}. Android is the most widely used tablet OS in 2016 \cite{netmarketshare:tablet_os}, and furthermore has the second largest diversity of manufacturers (13 and 194 different models in the source \cite{edbpriser:android}), only surpassed by Windows. Android was originally developed by Android Inc, but was bought by Google in 2005\cite{uk.complex:google_buys_android}, and has been continually developed by them since then. Android is known for its increased customizability compared to iOS
%% Windows tablets 
%( Acer Aspire Switch 11V
%  Asus Transformer Book T100HA
%  Dell Latitude 13 7000 series 2-in-1 (7350)
%  Dell Venue 8 Pro 3000 series
%  Getac F110
%  Lenovo IdeaPad Miix 700
%  Microsoft Surface Pro 4
%  HP Pavilion x2
%  HP Spectre x2
%  Kilde: http://www.pcmag.com/roundup/310159/the-best-windows-tablets
%)
\textbf{Windows}\newline
October 21st 2010 Microsoft released their first iteration of their current attempt into the smartphone market, called Windows Phone 7.\cite{techradar:winphone7_releasedate} With an incredibly tough competition at the time when iOS4 and Android 2.3 "Gingerbread" it performed fairly well. Microsoft made a very robust system with minimal crashes and slowdowns, this 
% Summarization.
% Linux - (???)
% Blackberry (is it even still relevant? - was it ever?)


