\section{State of the Art}

SEGES company \todo{Add Source. (https://www.seges.dk) (11/10/2013)}

SEGES is a danish company trying to bridge the gap between the latest agricultural research and the practicality of the profession. This makes them the go to information source for danish farmers, weather they only do live stock, farming or just does the economics of running a farm land is no issue, since SEGES have tools for mostly every situation. They are trying to stay as relevant as possible by participating in both national and international projects. 
SEGES is a fairly large company consisting of about 650 people and cover almost every part of the pipeline that is the agricultural profession. They even have an academic educational part, simply called SEGES Academy. SEGES is a very component based company. They have segmented their internal force into several specializations, such as: Software \& IT, Crops \& Environment, Business finance \& management, Dairy \& Beef etc. \unsure{Revisit. Sounds a bit too much like "These guys are the best EVER"}
In regards to their Software \& IT department, SEGES supply a lot of different specialized tools to the farmers in form of mobile or desktop applications, such as "Mark Online" \todo{Add source to: https://www.seges.dk/produkter/software/plante/mark-online} that is available in four different versions: Light, Basic, Plus and Premium. Every subsequent version costs more than the previous, but also unlocks additional features in the application. This chopping up the software in paid versions is reflected into all of their software tools and is reportedly \todo{Citation Needed} directly linked to the farmers DLBR-account \todo{Foot note here to DLBR explanation}. 
This componentialization of the different information sources that SEGES is doing can become quite difficult to navigate for the user and this could easily be improved by having a centralized application that collect and display all the relevant data for the user. SEGES have tried to do this with their Farm Tracking mobile application, but it is not perfect in the sense that it can become more user friendly and it doesn't contain all information that you might need, such as the farmers current inventory.

DLBR Company \todo{Add source. (http://www.dlbr.dk)}
DLBR is a danish community of 32 independent counselling companies. It is very common for danish farmers to have a DLBR-account. \todo{Citation Needed (as an interview)} 

% DLBR ( TLDR )
% (Dansk Landbrugsrådgivning)

% (possible weakness)
% This chopping up the software in paid versions is reflected into all of their software tools.

% Praise (short)
% Explanation of the size of the company
% - What software tools do they provide?
% Explain what DLBR is
% What weaknesses do they have?

% "Mange tak for de fine kommentarer, Özmir!"
