\textbf{Analysis of the interview}\label{interview_analysis}\unsure{Maybe a new title?}\newline
In this part we will analyze the interview found in appendix in chapter \ref{transscript:jens_ole} with regard to figuring out the problems that our interviewee had and requirements that our interviewee had to the product. 

The translations of the interviews below are focused on maintaining the meaning of the sentence, and have been reformulated to improve readability over the raw transcription data, which is available (in Danish) in the appendix in chapter \ref{transscript:jens_ole}.

% ----------------------------
"we're using Apple and we also use Android [...] my take on it is that Apple is just not usable, because we have a lot of Excel documents, and post-processing, and such, and that just doesn't work with Apple"\newline
%It is our understanding that he prefers Android.\newline
%We understand this as if he prefers Android.
% ----------------------------
"All GPS-functions would already be in this tablet, so you wouldn't have to input where you are manually"\newline
% ----------------------------
"[...] Then you could extract the data via USB [...] you plug in the USB-cable, and then choose that this is a John Deere"\newline
% ----------------------------
"And then you could visit a tractor dealer, for example Ferguson, and ask them 'How do I move the data from the tractor and out', and then they might be able to tell you that you can use this or that program to extract it"\newline
% ----------------------------
"[...] then you could go a step further and say that the farmer that doesn't use our machine rental normally, still can use the program, and if he then decides to use our services then we could just log on his, or extract the data [...]"\newline
% ----------------------------

Based on the interview segments above we have constructed the following list of program requirements:
\begin{itemize}[noitemsep]
    \item The program should be able to gather, calculate and show statistik on any customers field.
    \item The application should run on a handheld device.
    \item GPS-tracking should be integrated in the application.
    \item The application should be able to gather information from other software sources.
    \item Users should be able to have individual profiles.
    \item The application should be able to import and export data from/to excel compatible files.
    \item The application should be able to communicate with other clients.
\end{itemize}

We have likewise constructed a list of problems described in the interview:
\begin{itemize}[noitemsep]
    \item It's currently a rather intricate affair to make documentation for accounting purposes.
    \item Current systems are segmented and each use their own proprietary system.
    \item System integration with Apple products is problematic, the customer does not wish to use Apple products. % not really a problem, vi vælger Android
\end{itemize}

% programkrav
% X -Android (første citat)
% X -GPS (andet citat)
% X -samling af information fra andre software-kilder. (John Deere, SEGES, Claas) (tredje + fjerde citat)
% X -Login system (profil system) (indirekte indikeret i femte citat)
% X -Han vil gerne have direkte kontakt med HANS kunders profiler. (femte citat)
% X -Landmanden skal også selv kunne bruge programmet. (femte citat)
% X -Easy to Use. (bliver ikke nævnt direkte på noget tidspunkt i interviewet, men er implicit forventet fra den overordnede samtale)
